\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-02-19 investigation/docs/overview.tex
updtaes to scripts and report

\begin{table}[ht]
\centering
\begin{tabular}{rllllllllrlll}
  \hline
 & probename & snp1 & snp2 & nclass9 & minclass5 & LD01 & nsnpspass & nsnps & filter & lambda & nthres & nadjthres \\ 
  \hline
1 & ILMN\_1651385 & rs7989895 & rs4846085 & 419387 & 285750 & 506818 & 269121 & 506818 & 1.00 & 1.61 & 4 & 0 \\ 
  2 & ILMN\_1651705 & rs872311 & rs11032695 & 419021 & 278721 & 511121 & 260851 & 511121 & 1.00 & 1.12 & 1 & 0 \\ 
  3 & ILMN\_1651886 & rs7108734 & rs12784396 & 427787 & 319167 & 501291 & 305496 & 501291 & 1.00 & 1.07 & 0 & 0 \\ 
  4 & ILMN\_1652333 & rs898095 & rs9892064 & 442554 & 336649 & 515007 & 322786 & 515007 & 2.00 & 1.34 & 7 & 0 \\ 
  5 & ILMN\_1653205 & rs12429804 & rs2896452 & 383323 & 213815 & 507099 & 183628 & 507099 & 1.00 & 1.78 & 24 & 4 \\ 
  6 & ILMN\_1653205 & rs12454561 & rs2896452 & 386460 & 215536 & 511390 & 185098 & 511390 & 1.00 & 1.78 & 25 & 4 \\ 
  ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ 
   \hline
\end{tabular}
\caption*{Header of summary output for 501 pairs}
\end{table}
\end{landscape}

>>>>

\begin{table}[ht]
\centering
\tiny
\begin{tabular}{llllllllrrrlllllll}
  \hline
 probename & snp1 & snp2 & nclass9 & minclass5 & LD01 & npass & nsnps & filter & p\_egcut & p\_fehr & $\lambda$ & nthres & Fe & N\_Fe & F\_emp & P\_emp & type1 \\ 
  \hline
ILMN\_1651385 & rs7989895 & rs4846085 & 419387 & 285750 & 506818 & 269121 & 506818 & 1.00 & 0.25 & 0.61 & 1.61 & 4 & 9.43 & 0 & 8.95 & 6.35 & 0.10 \\ 
ILMN\_1651705 & rs872311 & rs11032695 & 419021 & 278721 & 511121 & 260851 & 511121 & 1.00 & 0.30 & 0.26 & 1.12 & 1 & 9.41 & 0 & 7.75 & 5.41 & 0.05 \\ 
ILMN\_1651886 & rs7108734 & rs12784396 & 427787 & 319167 & 501291 & 305496 & 501291 & 1.00 & 0.01 & 0.21 & 1.07 & 0 & 9.5 & 0 & 7.4 & 5.13 & 0.05 \\ 
ILMN\_1652333 & rs898095 & rs9892064 & 442554 & 336649 & 515007 & 322786 & 515007 & 2.00 & 29.39 & 28.24 & 1.34 & 7 & 9.53 & 0 & 9.48 & 6.77 & 0.07 \\ 
ILMN\_1653205 & rs12429804 & rs2896452 & 383323 & 213815 & 507099 & 183628 & 507099 & 1.00 & 0.02 & 0.29 & 1.78 & 24 & 9.22 & 4 & 10.56 & 7.63 & 0.11 \\ 
ILMN\_1653205 & rs12454561 & rs2896452 & 386460 & 215536 & 511390 & 185098 & 511390 & 1.00 &  & 0.31 & 1.78 & 25 & 9.22 & 4 & 10.56 & 7.63 & 0.11 \\ 
ILMN\_1653205 & rs2896452 & rs1004564 & 373839 & 208706 & 494954 & 179170 & 494954 & 1.00 & 0.18 & 0.38 & 1.78 & 23 & 9.2 & 2 & 10.08 & 7.25 & 0.11 \\ 
ILMN\_1653205 & rs7152284 & rs2896452 & 385471 & 215221 & 509793 & 184859 & 509793 & 1.00 & 0.07 & 2.18 & 1.78 & 23 & 9.22 & 3 & 10.56 & 7.63 & 0.11 \\ 
ILMN\_1653205 & rs8051751 & rs2896452 & 386341 & 215644 & 511501 & 185188 & 511501 & 1.00 & 0.18 & 1.39 & 1.78 & 24 & 9.22 & 4 & 10.56 & 7.63 & 0.11 \\ 
ILMN\_1654545 & rs4333645 & rs1455268 & 421112 & 307876 & 495374 & 294544 & 495374 & 2.00 & 0.01 & 0.10 & 1.45 & 4 & 9.48 & 0 & 9.14 & 6.5 & 0.08 \\ 
ILMN\_1656378 & rs10906857 & rs12490878 & 418379 & 314668 & 489831 & 301252 & 489831 & 1.00 & 0.34 & 0.42 & 1.1 & 1 & 9.49 & 0 & 7.69 & 5.36 & 0.05 \\ 
ILMN\_1658247 & rs11613438 & rs1047944 & 402228 & 251785 & 490871 & 234981 & 490871 & 2.00 & 1.55 & 1.27 & 1.53 & 21 & 9.35 & 1 & 9.73 & 6.97 & 0.09 \\ 
   \hline
\end{tabular}
\caption*{Header of summary output for 501 pairs}
\end{table}

\end{landscape}
